InteroceptionStudy_GPValidation

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

@@

```
process gazepath and ledalab
```{r}
library(gazepath)
GUI()

>>>>

  setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/GP_IAPS_for_gazepath/346_355")

@@

process gazepath and ledalab

gazepath settings

left eye x coord: left_gaze_x_cor_pix
left eye y coord: left_gaze_y_cor_pix

didtance: distance (mm)

right eye x coord: right_gaze__cor_pix
right eye y coord: right_gaze_x_cor_pix
didtance: distance (mm)

trial index: trialnq

sample rate: 150
screen resolution height (pix): 1200
screen resolution width (pix): 1920

stimuli height (px): 768
stimuli width (px): 1024
variables to keep: trial unq

install.packages('gazepath')
library(gazepath)
GUI()
